Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-25 Thesis/03-chap3.qmd
imporve lang in residual dist

One of the assumptions of the classical normal linear regression model is that the error $\boldsymbol{e}$ follows a multivariate normal distribution with zero mean and constant variance, i.e., $\boldsymbol{e} \sim N(\boldsymbol{0}_n,\sigma^2\boldsymbol{I}_n)$. It can be known that residuals $\hat{\boldsymbol{e}}$ also follow a certain probability distribution transformed from the multivariate normal distribution, which will be denoted as $Q$. This reference distribution $Q$ summarizes what "good" residuals should follow given the design matrix $\boldsymbol{X}$ is known and fixed.

>>>>

One of the assumptions of the classical normal linear regression model is that the error $\boldsymbol{e}$ follows a multivariate normal distribution with zero mean and constant variance, i.e., $\boldsymbol{e} \sim N(\boldsymbol{0}_n,\sigma^2\boldsymbol{I}_n)$. It follows that the distribution of residuals $\hat{\boldsymbol{e}}$ can be characterized by a certain probability distribution, denoted as $Q$, which is transformed from the multivariate normal distribution. This reference distribution $Q$ summarizes what "good" residuals should follow given the design matrix $\boldsymbol{X}$ is known and fixed.
